Evaluative adjective sentences: \\ A question-based analysis of projection

### 2019-04-17 paper/paper-anon.tex
added exp3 data and rscripts

%From Mandy conversation:
%- add sentence on p.15 that this meaning is not the final version
%- section 3.2: more nuanced discussion about whether previous analyses assume that prejacent is entailed
%- unacceptable because contradictory: no imaginable circumstance where not-prejacent but S
%- 23c is odd for mandy, perhaps need footnote
%- "will" is part of the prejacent for judging the entailments in 23
%- Mandy wants "enough" even in positive example 23b so "enough" has nothing to do with negation or projection

\title{Evaluative adjective sentences: \\ A question-based analysis of projection\thanks{For helpful comments and critical feedback, we thank David Beaver, Ashwini Deo, Lauri Karttunen, Stanley Peters, Craige Roberts,
Stephanie Solt and the audiences at the following venues: the 6th meeting of the DFG Network
{\em Questions in Discourse} at the University of G\"ottingen, 
the University of Stuttgart, the 16th Sklarska Poreba workshop, the
Redrawing Pragmasemantic Borders workshop at the University of
Groningen, the University of Cologne, Oxford University, the University of T\"ubingen,  the University of G\"ottingen, the {\em
Experimental Pragmatics} 2015 conference in Chicago, The Ohio State
University and Cornell University. We thank Willy Cheung for his assistance with the corpus study. We gratefully acknowledge
financial support from the {\em National Science Foundation} (grants
BCS-0952571 and BCS-1452674), the Alexander von Humboldt Foundation and the Ohio State
University College of Arts and Sciences Targeted Investment in
Excellence initiative.}}

\author[$\circ$]{Judith Tonhauser}
\author[$\bullet$]{Judith Degen}
\author[$\circ$]{Marie-Catherine de Marneffe}
\author[$\star$]{Mandy Simons}

\affil[$\circ$]{The Ohio State University}
\affil[$\bullet$]{Stanford University}
\affil[$\star$]{Carnegie Mellon University}

\renewcommand\Authands{ and }

@@

@@

Evaluative adjective sentences are standardly analyzed as presupposing the prejacent: for instance, {\em Kim wasn't smart to
watch the movie} is taken to presuppose that Kim watched the movie
(e.g., \citealt{norrick78,barker02,oshima09b,kertz2010}). This paper argues against an analysis of the prejacent as a lexically-specified presupposition and proposes instead that the projectivity of the prejacent depends on the question addressed by the utterance of the evaluative adjective sentence (\citealt{beaver-clark08,best-question,brst-ar}). Evidence for the proposed analysis comes from a study of the projectivity of the prejacent in naturally occurring evaluative adjective sentences and two experiments that show that the at-issueness and projectivity of the prejacent are sensitive to the question addressed by the utterance of the evaluative adjective sentence. The proposed analysis is also compared with that of \citealt{karttunen-etal2014}, according to which evaluative adjective sentences are systematically ambiguous.

@@

In an evaluative adjective sentence (EAS) like (\ref{f}), the
evaluative adjective {\em stupid} subcategorizes for a non-pleonastic subject noun
phrase ({\em Feynman}) and a {\em to-}infinitive ({\em to
dance on the table}); the subject of the predicate {\em be stupid} is the understood subject of the {\em to-}infinitive (e.g., \citealt{wilkinson70, norrick78,barker02,kertz2010}). Two contents of EASs that this paper is concerned with are the `prejacent' and the `evaluation': in (\ref{f}), the prejacent is that Feynman danced on the table and the evaluation is that 
Feynman dancing on the table was stupid.\footnote{This paper ignores the subject-related presuppositions discussed in \citealt{barker02}.}

\begin{exe} \ex\label{f} Feynman was stupid to dance on the table. \hfill (\citealt[18]{barker02})

EASs have traditionally been analyzed as presupposing the prejacent (e.g., \citealt{norrick78,barker02,oshima09b,kertz2010}). On such analyses,  evaluative adjectives like {\em stupid} lexically specify that the prejacent
must be entailed by or satisfied in the common ground of the interlocutors in
order for an EAS to be interpretable (e.g.,
\citealt{heim83,vds92}). Such analyses are motivated by and straightforwardly account for examples like those in (\ref{f2}a-d) in which the prejacent projects over entailment-canceling operators, i.e., negation in (\ref{f2}a), a polar question in (\ref{f2}b), the possibility adverb {\em perhaps} in (\ref{f2}c) and the antecedent of the conditional in (\ref{f2}d). That is, speakers who utter (\ref{f2}a-d) may be taken to be committed to the prejacent, that Feynman danced on the table, even though the evaluative adjective occurs under an entailment-canceling operator. The evaluation, on the other hand, that Feyman dancing on the table was stupid, is not projective content but denied in (\ref{f2}a), questioned in (\ref{f2}b), and merely considered a possibility in (\ref{f2}c) and (\ref{f2}d).

@@

Recently, \citet{karttunen-etal2014} provided naturally occurring examples that show that utterances of sentences in which the evaluative adjective is embedded under negation can receive interpretations according to which the prejacent
does not project, but is interpreted in the scope of negation. For instance, the speaker of (\ref{nat}a) is not committed to living close to their parents and instead communicates that they do not live close to their parents. Likewise, the speaker of (\ref{nat}b) is not committed to having stumbled through the junkyard in the dark but rather communicates that they did not stumble through the junkyard.

@@

We discuss below why such examples are problematic for analyses according to which the prejacent is a presupposition. But we first need to mention that even though all native speakers of American English appear to be able to retrieve the intended interpretations of examples like (\ref{nat}), a sizeable portion strongly prefers to realize such interpretations with variants that includes {\em enough}, as in {\em I wasn't stupid enough to go stumbling through the junkyard in the dark} for (\ref{nat}b); see also \citealt{karttunen2013} and \citealt{karttunen-etal2014} for this observation. Our goal in this paper is to analyze the interpretation of EASs and we assume that all native speakers of American English have access to both interpretations, that is, an interpretation according to which the prejacent projects, as in (\ref{f2}), and an interpretation according to which it doesn't project, as in (\ref{nat}). Evidence that examples in which the prejacent does not project are part of the productive language use of some native speakers of American English comes from the existence of naturally occurring examples like (\ref{nat}); further  such examples are presented in this paper. Additional evidence comes from the fact that the audiences to which this research was presented over the years always included native speakers that judged examples like (\ref{nat}) to be perfectly acceptable. More systematic evidence for the existence of such speakers comes from the acceptability rating study presented in Appendix \ref{s-acc}: of the 94 self-reported native speakers of American English that participated in the study, about 20-30\% judged negated evaluative adjective sentences without {\em enough} to be acceptable under a non-projecting interpretation of the prejacent. We return to the observed variation among native speakers of American English in section \ref{s5}.

To account for examples like (\ref{nat}), in which the prejacent is not a commitment of the speaker, presuppositional analyses appeal to local accommodation, a process whereby a presupposition is added to a local context, such as the context created by negation: presuppositions can be locally accommodated if adding the presupposition to the common ground of the interlocutors (a process known as global accommodation) would result in a contradiction, uninformativity or problems with
binding (\citealt{heim82,vds92}). In example (\ref{nat}a), for instance, the prejacent is locally accommodated under negation because globally accommodating the prejacent in the common ground would result in a contradiction: the prejacent is that the speaker lived close to their parents, but, according to the context, the closest that the speaker lived to their parents was when the speaker lived in Denver, Colorado, i.e., about 300 miles (480 km) away from their parents in Garden City, Kansas. The prejacent is correctly predicted to be locally accommodated in (\ref{nat}a), i.e., does not become a commitment of the speaker.

Examples like (\ref{nat}) point to two problems for analyses according to which the prejacent is a presupposition. The first problem concerns the prejacent. In example (\ref{nat}b), globally accommodating the prejacent does not result in a contradiction, uninformativity or problems with
binding: if the prejacent was added to the common ground,
(\ref{nat}b) would mean that the speaker knew that someone was in the
junkyard, that they stumbled through the junkyard and got hurt, and that
the speaker does not consider these actions stupid (perhaps because these actions
led to the person in the junkyard receiving help). Because such an interpretation does not result in a contradiction, uninformativity or problems with
binding, analyses that take the prejacent to be a presupposition incorrectly  predict that the prejacent of (\ref{nat}b) is globally accommodated, i.e., is a commitment of the speaker.\footnote{It may be possible to account for the non-projection of the prejacent on the basis of plausibility considerations: \citealt[162]{vonfintel08}, for instance,  proposed that ``what gets accommodated depends on the best guess of the hearers about what the speaker might have intended as the adjustment to the common ground that would admit the asserted sentence''. From this perspective, the cues to the projectivity of the prejacent identified in this paper may help flesh out the reasoning process that hearers and readers undergo in interpreting EASs. Plausibility considerations do not, however, address the second problem that presuppositional analyses face.}

The second problem concerns the evaluation. What is remarkable is that in negated evaluative adjective sentences (NEASs) in which the prejacent is interpreted in the semantic scope of negation, as in (\ref{nat}), the evaluation is not negated but counterfactual. That is, (\ref{nat}a) does not mean that the speaker did not live extremely close to their parents and that it is not fortunate for the speaker to live close to their parents. Rather, (\ref{nat}a) means that the speaker did not live extremely close to their parents and that it would be fortunate for the speaker to live close to their parents. Likewise, (\ref{nat}b) does not mean that the speaker did not stumble through the junkyard and that it is not stupid for the speaker to stumble through the junkyard. Rather, (\ref{nat}b) means that the speaker did not stumble through the junkyard and that it would be stupid for the speaker to stumble through the junkyard. Thus, in NEASs in which the prejacent projects, as in (\ref{f2}a), the evaluation is negated, and in examples in which the prejacent does not project, as in (\ref{nat}), the evaluation is counterfactual.

This behavior of the evaluation is not predicted by the two analyses that consider content other than the prejacent: \citealt{oshima09b} and \citealt{barker02}. In \citealt{oshima09b}, the prejacent is a presupposition and what is asserted is the following complex content: from the prejacent it can be inferred that the denotation of the subject is in the extension of the evaluative adjective (p.371). That is, (\ref{f2}a) is correctly predicted to presuppose that Feynman danced on the table and to assert that it cannot be inferred from Feynman dancing on the table that Feyman is stupid. Similarly then, (\ref{nat}b) is predicted to convey that the speaker did not stumble through the junkyard (the prejacent is locally accommodated) and to assert that it cannot be inferred from the speaker stumbling through the junkyard that the speaker is stupid. This assertion is too weak: crucially, it does not follow the speaker stumbling through the junkyard would be stupid.

According to \citepos{barker02} dynamic semantic analysis, the update effect of a NEAS like (\ref{f2}a) is to filter out those worlds in which the contextual standard of {\em stupid} is too high for Feynman's participation in the event of dancing on the table to count as stupid (p.25). In other words, only those worlds remain in which Feynman dancing on the table is not considered stupid. Similarly then, the update effect of (\ref{nat}b), in which the prejacent is locally accommodated under negation, is to filter out those worlds in which the contextual standard of {\em stupid} is too high for the speaker's participation in the event of stumbling through the junkyard to count as stupid. In other words, only those worlds remain in which the speaker does not stumble through the junkyard and in which the speaker stumbling through the junkyard is not stupid. However, as discussed above, this is not what (\ref{nat}b) is understood to mean. In sum, analyses of EASs according to which the prejacent is a presupposition do not account for examples like (\ref{nat}) in which the prejacent is interpreted in the scope of negation, but the evaluation is not.

\citet{karttunen-etal2014}, who pointed out that the prejacent need not project, account for the two interpretations of EASs by proposing that evaluative adjectives are ambiguous: one lexical entry ({\em adj}$_1$) derives the presupposition and assertion in (\ref{lex}a) and the second lexical entry ({\em adj}$_2$) derives the presupposition and assertion in (\ref{lex}b).

\begin{exe}
\ex\label{lex} \citealt[249]{karttunen-etal2014}: Presuppositions and assertions of EASs 
\begin{xlist}
\ex {\em adj}$_1$
\\ Presupposed content: NP VPed
\\ Asserted content: For NP to VP would be Adj

@@

\end{xlist}
\end{exe}
The lexical entry in (\ref{lex}a) predicts that an utterance of the NEAS in (\ref{f2}a) presupposes that Feynman danced on the table and asserts that it is not the case that for Feynman to dance on the table would be stupid. What follows from the presupposed and the asserted content, according to \citealt[248]{karttunen-etal2014}, is that it is not the case that Feynman dancing on the table was stupid, i.e., what we have called the evaluation. In contrast, the lexical entry in (\ref{lex}b) predicts that an utterance of the NEAS in (\ref{nat}b) presupposes that for the speaker to stumble through the junkyard would be stupid and for the speaker to not stumble through the junkyard would not be stupid, and asserts that it is not the case that what the speaker did about stumbling through the junkyard was stupid. Thus, what we have called the evaluation, that the speaker stumbling through the junkyard would be stupid, is part of the presupposed content under \citepos{karttunen-etal2014} analysis. That the prejacent is negated (the speaker didn't stumble through the junkyard) follows, according to \citealt[249]{karttunen-etal2014}, from what is presupposed and what is asserted.

\citepos{karttunen-etal2014} analysis improves over previous analyses because it is able to derive both attested interpretations. But the analysis comes at a cost: first, evaluative adjectives are systematically ambiguous, and, second, as we argue in section \ref{s3}, it misses out on an empirical generalization about how common ground information  influences the interpretation of EASs. In this paper, we develop an analysis of EASs that accounts for the two interpretations with a single lexical entry for evaluative adjectives. The crux of the analysis is that evaluative adjectives do not lexically specify that the prejacent is a presupposition. In section \ref{s2}, we show, based on a study of naturally occurring NEASs, that the prejacent is not highly projective. We take this to provide empirical support for not analyzing the prejacent as a lexically-specified presupposition. In section \ref{s3}, we present an analysis of EASs according to which the projectivity of the prejacent of an utterance in which the evaluative adjective is embedded under an entailment-canceling operator is predicted by the extent to which the prejacent is at-issue with respect to the Discourse Question addressed by the utterance. We test three predictions of the analysis in section \ref{s4} and discuss two open issues in section \ref{s5}. The paper concludes in section \ref{s6}.

\section{Experiment 1: Projectivity of the prejacent in naturally occurring NEAS}\label{s2}

\citet{karttunen-etal2014} provided naturally occurring examples that showed that the prejacent of NEASs need not project. The goal of the study we present in this section was to more systematically explore how projective the prejacent is in naturally occurring NEAS. Following \citealt{tbd-variability}, we assume that projectivity is a gradient property of utterance content: the more the speaker or author of the utterance is taken to be committed to the truth of an utterance content, the more projective the content is. To explore the projectivity of the prejacent, native speakers of American English were presented with naturally occurring NEAS and asked to rate the projectivity of the prejacent.\footnote{\label{f-git}The
materials, data and the R code for generating the figures and analyses of the experiments reported on in this paper are available at
\url{https://github.com/judith-tonhauser/evaluative-adjectives}.}

>>>>

\title{Evaluative adjective sentences: \\ A question-based analysis of projection}

%\thanks{For helpful comments and critical feedback, we thank David Beaver, Ashwini Deo, Lauri Karttunen, Stanley Peters, Craige Roberts,
%Stephanie Solt and the audiences at the following venues: the 6th meeting of the DFG Network
%{\em Questions in Discourse} at the University of G\"ottingen, 
%the University of Stuttgart, the 16th Sklarska Poreba workshop, the
%Redrawing Pragmasemantic Borders workshop at the University of
%Groningen, the University of Cologne, Oxford University, the University of T\"ubingen,  the University of G\"ottingen, the {\em
%Experimental Pragmatics} 2015 conference in Chicago, The Ohio State
%University and Cornell University. We thank Willy Cheung for his assistance with the corpus study and Timo Roettger for consultation on the Bayesian regression analysis. We gratefully acknowledge
%financial support from the {\em National Science Foundation} (grants
%BCS-0952571 and BCS-1452674), the Alexander von Humboldt Foundation and the Ohio State
%University College of Arts and Sciences Targeted Investment in
%Excellence initiative.}}

\author{}
%\author[$\circ$]{Judith Tonhauser}
%\author[$\bullet$]{Judith Degen}
%\author[$\circ$]{Marie-Catherine de Marneffe}
%\author[$\star$]{Mandy Simons}
%
%\affil[$\circ$]{The Ohio State University}
%\affil[$\bullet$]{Stanford University}
%\affil[$\star$]{Carnegie Mellon University}
%
%\renewcommand\Authands{ and }

@@

% length at beginning of revisions: 27,235 (monterrey), main body: 20,803
% length at end of revisions

@@

Two contents of evaluative adjective sentences, like {\em Kim was smart to watch the movie}, are the prejacent, that Kim watched the movie, and the generalization, that the degree to which Kim watching the movie is smart is higher than the contextual standard of {\em smart}. The prejacent is standardly analyzed as a presupposition: {\em Kim wasn't smart to
watch the movie} is taken to presuppose that Kim watched the movie
(e.g., \citealt{norrick78,barker02,oshima09b,kertz2010}). This paper argues against such analyses because, among other things, they do not capture an interaction between the prejacent and the generalization that has not yet been observed for projective content: when the prejacent projects, the generalization does not, and when the prejacent does not, the generalization does! We develop an analysis according to which the prejacent is not a lexically specified presupposition but projects if it is not at-issue with respect to the question addressed by the utterance of the evaluative adjective sentence. In addition to capturing the peculiar interaction between the prejacent and the generalization, our question-based projection analysis significantly expands on previous such analyses (e.g., \citealt{beaver-clark08,best-question,brst-ar,abrusan2011}) by incorporating a novel constraint on the question addressed by an utterance: the more an utterance content follows from the common ground, the less likely the question is about that content. We provide experimental evidence for the proposed analysis and argue that our analysis improves on that of \citealt{karttunen-etal2014}, according to which evaluative adjective sentences are systematically ambiguous.

@@

In an evaluative adjective sentence (EAS) like (\ref{f}), the
evaluative adjective {\em stupid} subcategorizes for a non-pleonastic subject noun
phrase ({\em Feynman}) and a {\em to-}infinitive ({\em to
dance on the table}); the subject of the predicate {\em be stupid} is the understood subject of the {\em to-}infinitive (e.g., \citealt{wilkinson70, norrick78,barker02,kertz2010}). One of the contents standardly discussed in the literature is (what we refer to as) the prejacent: in (\ref{f}), the prejacent is that Feynman danced on the table.\footnote{This paper ignores the subject-related presuppositions discussed in \citealt{barker02}.}

\begin{exe} 
\ex\label{f} Feynman was stupid to dance on the table. \hfill (\citealt[18]{barker02})
\end{exe} 
The prejacent has traditionally been analyzed as presupposition (e.g., \citealt{norrick78,barker02,oshima09b,kertz2010}). On formal analyses in this tradition, evaluative adjectives like {\em stupid} lexically specify that the prejacent
must be entailed by or satisfied in the common ground of the interlocutors in
order for an EAS to be interpretable (e.g.,
\citealt{heim83,vds92}). Such analyses are motivated by and straightforwardly account for examples like those in (\ref{f2}a-d) in which the prejacent projects over entailment-canceling operators, i.e., negation in (\ref{f2}a), a polar question in (\ref{f2}b), the possibility adverb {\em perhaps} in (\ref{f2}c) and the antecedent of the conditional in (\ref{f2}d). That is, speakers who utter (\ref{f2}a-d) may be taken to be committed to the prejacent, that Feynman danced on the table, even though the evaluative adjective is embedded under an entailment-canceling operator. 
%The evaluation, on the other hand, that Feynman dancing on the table was stupid, is not projective content but denied in (\ref{f2}a), questioned in (\ref{f2}b), and merely considered a possibility in (\ref{f2}c) and (\ref{f2}d).

@@

Recently, \citet{karttunen-etal2014} provided naturally occurring examples that show that utterances of sentences in which the evaluative adjective is embedded under negation can receive an interpretation according to which the prejacent
does not project, but is interpreted in the scope of negation. For instance, the speaker of (\ref{nat}a) is not committed to living close to their parents and instead communicates that they do not live close to their parents. Likewise, the speaker of (\ref{nat}b) is not committed to having stumbled through the junkyard in the dark but rather communicates that they did not stumble through the junkyard.

@@

We discuss below why such examples are problematic for analyses of the prejacent as a lexically specified presupposition. But we first need to mention that there is variation in the population of native speakers of American English: whereas all speakers are able to interpret EASs in which the prejacent does not project, i.e., are able to retrieve the intended interpretations of examples like (\ref{nat}), a sizeable portion strongly prefers to realize such interpretations with variants that includes {\em enough}, as in {\em I wasn't stupid enough to go stumbling through the junkyard in the dark} for (\ref{nat}b); see also \citealt{karttunen2013} and \citealt{karttunen-etal2014} for this observation. Nevertheless, EASs in which the prejacent does not project are part of American English, as evidenced by the existence of naturally occurring examples like (\ref{nat}); further  such examples are presented in this paper. Additional evidence comes from the fact that there are native speakers who judge such EASs to be perfectly acceptable\footnote{The audiences to which this research was presented over the years always included native speakers that judged examples like (\ref{nat}) to be acceptable. More systematic evidence for the existence of such speakers comes from the acceptability rating study presented in Appendix \ref{s-acc}: of the 94 self-reported native speakers of American English that participated in the study, about 20-30\% judged negated evaluative adjective sentences without {\em enough} to be acceptable under a non-projecting interpretation of the prejacent.} and who produce examples like (\ref{nat}). We therefore assume that all native speakers of American English are able to retrieve both interpretations of EASs even if they might not produce EASs in which the prejacent does not project. Our goal in this paper is to analyze the interpretation of EASs; we briefly return to the observed variation among native speakers of American English in section \ref{s5}.

To account for examples like (\ref{nat}), in which the prejacent is not a commitment of the speaker, presupposition analyses appeal to local accommodation, a process whereby a presupposition is added to a local context, such as the context created by negation: presuppositions can be locally accommodated if adding the presupposition to the common ground of the interlocutors (a process known as global accommodation) would result in a contradiction, uninformativity or problems with
binding (\citealt{heim82,vds92}). In example (\ref{nat}a), for instance, the prejacent is locally accommodated under negation because globally accommodating the prejacent in the common ground would result in a contradiction: the prejacent is that the speaker lived close to their parents, but, according to the context, the closest that the speaker lived to their parents was when the speaker lived in Denver, Colorado, i.e., about 300 miles (480 km) away from their parents in Garden City, Kansas. The prejacent is correctly predicted to be locally accommodated in (\ref{nat}a), i.e., does not become a commitment of the speaker.

Negated evaluative adjective sentences (NEASs) like (\ref{nat}) point to two problems for analyses according to which the prejacent is a presupposition. The first problem concerns the prejacent. In example (\ref{nat}b), globally accommodating the prejacent does not result in a contradiction, uninformativity or problems with
binding: if the prejacent was added to the common ground,
(\ref{nat}b) would mean that the speaker knew that someone was in the
junkyard, that they stumbled through the junkyard and got hurt, and that
the speaker does not consider these actions stupid (perhaps because these actions
led to the person in the junkyard receiving help). Because such an interpretation does not result in a contradiction, uninformativity or problems with
binding, analyses that take the prejacent to be a presupposition incorrectly  predict that the prejacent of (\ref{nat}b) is globally accommodated, i.e., is a commitment of the speaker.\footnote{It may be possible to account for the non-projection of the prejacent on the basis of plausibility considerations: \citealt[162]{vonfintel08}, for instance,  proposed that ``what gets accommodated depends on the best guess of the hearers about what the speaker might have intended as the adjustment to the common ground that would admit the asserted sentence''. The cues to the projectivity of the prejacent identified in the following sections may help flesh out the reasoning process that hearers and readers undergo in interpreting EASs. Plausibility considerations do not, however, address the second problem that presuppositional analyses face.}

The second problem concerns content other than the prejacent: here, the two previous analyses that explicitly consider content other than the prejacent, \citealt{oshima09b} and \citealt{barker02}, do not make sufficiently strong predictions. Consider first \citealt{oshima09b}. On this analysis, the prejacent is a presupposition and what is asserted is the following complex content: from the prejacent it can be inferred that the denotation of the subject is in the extension of the evaluative adjective (p.371). That is, (\ref{f2}a) is predicted to presuppose that Feynman danced on the table and to assert that it cannot be inferred from Feynman dancing on the table that Feynman is stupid. Similarly then, (\ref{nat}b) is predicted to convey that the speaker did not stumble through the junkyard (if the prejacent is locally accommodated) and to assert that it cannot be inferred from the speaker stumbling through the junkyard that the speaker is stupid. This assertion is too weak: (\ref{nat}b) means that the speaker stumbling through the junkyard would be stupid. Next consider \citealt{barker02}: on this dynamic semantic analysis, the update effect of a NEAS like (\ref{f2}a) is to filter out those worlds in which the contextual standard of {\em stupid} is too high for Feynman's participation in the event of dancing on the table to count as stupid (p.25); only those worlds remain in which Feynman dancing on the table is not considered stupid. Similarly then, the update effect of (\ref{nat}b), in which the prejacent is locally accommodated, is to filter out those worlds in which the contextual standard of {\em stupid} is too high for the speaker's participation in the event of stumbling through the junkyard to count as stupid. The worlds that remain are ones in which the speaker does not stumble through the junkyard and in which the speaker stumbling through the junkyard is not stupid. However, as mentioned above, this is not what (\ref{nat}b) is understood to mean.

%The second problem concerns the evaluation. What is remarkable is that in negated evaluative adjective sentences (NEASs) in which the prejacent is interpreted in the semantic scope of negation, as in (\ref{nat}), the evaluation is not negated but counterfactual. That is, (\ref{nat}a) does not mean that the speaker did not live extremely close to their parents and that it is not fortunate for the speaker to live close to their parents. Rather, (\ref{nat}a) means that the speaker did not live extremely close to their parents and that it would be fortunate for the speaker to live close to their parents. Likewise, (\ref{nat}b) does not mean that the speaker did not stumble through the junkyard and that it is not stupid for the speaker to stumble through the junkyard. Rather, (\ref{nat}b) means that the speaker did not stumble through the junkyard and that it would be stupid for the speaker to stumble through the junkyard. Thus, in NEASs in which the prejacent projects, as in (\ref{f2}a), the evaluation is negated, and in examples in which the prejacent does not project, as in (\ref{nat}), the evaluation is counterfactual. 
%
%This behavior of the evaluation is not predicted by the two analyses that consider content other than the prejacent: \citealt{oshima09b} and \citealt{barker02}. Consider first \citealt{oshima09b}. On this analysis, the prejacent is a presupposition and what is asserted is the following complex content: from the prejacent it can be inferred that the denotation of the subject is in the extension of the evaluative adjective (p.371). That is, (\ref{f2}a) is correctly predicted to presuppose that Feynman danced on the table and to assert that it cannot be inferred from Feynman dancing on the table that Feynman is stupid. Similarly then, (\ref{nat}b) is predicted to convey that the speaker did not stumble through the junkyard (the prejacent is locally accommodated) and to assert that it cannot be inferred from the speaker stumbling through the junkyard that the speaker is stupid. This assertion is too weak as (\ref{nat}b) means that the speaker stumbling through the junkyard would be stupid. Next consider \citealt{barker02}: on this Next consider \citealt{barker02}: on this dynamic semantic analysis, the update effect of a NEAS like (\ref{f2}a) is to filter out those worlds in which the contextual standard of {\em stupid} is too high for Feynman's participation in the event of dancing on the table to count as stupid (p.25). In other words, only those worlds remain in which Feynman dancing on the table is not considered stupid. Similarly then, the update effect of (\ref{nat}b), in which the prejacent is locally accommodated under negation, is to filter out those worlds in which the contextual standard of {\em stupid} is too high for the speaker's participation in the event of stumbling through the junkyard to count as stupid. In other words, only those worlds remain in which the speaker does not stumble through the junkyard and in which the speaker stumbling through the junkyard is not stupid. However, as discussed above, this is not what (\ref{nat}b) is understood to mean. In sum, analyses of EASs according to which the prejacent is a presupposition do not account for examples like (\ref{nat}) in which the prejacent is interpreted in the scope of negation, but the evaluation is not. 
%
%
%According to \citepos{barker02} dynamic semantic analysis, the update effect of a NEAS like (\ref{f2}a) is to filter out those worlds in which the contextual standard of {\em stupid} is too high for Feynman's participation in the event of dancing on the table to count as stupid (p.25). In other words, only those worlds remain in which Feynman dancing on the table is not considered stupid. Similarly then, the update effect of (\ref{nat}b), in which the prejacent is locally accommodated under negation, is to filter out those worlds in which the contextual standard of {\em stupid} is too high for the speaker's participation in the event of stumbling through the junkyard to count as stupid. In other words, only those worlds remain in which the speaker does not stumble through the junkyard and in which the speaker stumbling through the junkyard is not stupid. However, as discussed above, this is not what (\ref{nat}b) is understood to mean. In sum, analyses of EASs according to which the prejacent is a presupposition do not account for examples like (\ref{nat}) in which the prejacent is interpreted in the scope of negation, but the evaluation is not.

\citepos{karttunen-etal2014} analysis improves on previous ones because it is able to derive both attested interpretations. It does so by assuming that evaluative adjectives are ambiguous: the prejacent is specified as presupposed in the lexical entry in  (\ref{lex}a) but not in (\ref{lex}b).

\begin{exe}
\ex\label{lex} \citealt[249]{karttunen-etal2014}: Presuppositions and assertions of EASs of the form `NP was Adj to VP'
\begin{xlist}
\ex {\em adj}$_1$
\\ Presupposed content: NP VPed
\\ Asserted content: For NP to VP would be Adj

@@

% if generalization "for NP to VP is/would be Adj" follows from CG, we predict that prejacent is at-issue, i.e., doesn't project
% K et al predict for consonant NEAS that adj2 is used, i.e., prejacent doesn't project

% if CG is neutral wrt generalization "for NP to VP is/would be Adj", we predict that prejacent or generalization could project

% if negation of generalization follows from CG, we predict that prejacent is not-at-issue, i.e., projects
% K et al predict for dissonant NEAS that adj1 is used, i.e., prejacent projects

% for us: which content is at-issue is influenced by what follows from CG
% for K et al: which lexical entry is used is influenced by what follows from CG

%{\bf Adj1: prejacent presupposed, evaluation asserted, so it doesn't project}
%
%{\bf Adj2: evaluation presupposed, asserted content is under negation, so prejacent is denied, doesn't project}

The lexical entry in (\ref{lex}a) correctly predicts that the NEAS in (\ref{f2}a) has an interpretation according to which the prejacent, that  Feynman danced on the table, projects. Furthermore, what is asserted is that it is not the case that for Feynman to dance on the table would be stupid, from which it follows, together with the prejacent,  that it is not the case that Feynman dancing on the table was stupid (\citealt[248]{karttunen-etal2014}). In contrast, the lexical entry in (\ref{lex}b) predicts that the NEAS in (\ref{nat}b) has an interpretation according to which it is presupposed that for the speaker to stumble through the junkyard would be stupid and for the speaker to not stumble through the junkyard would not be stupid; thus, in contrast to \citepos{oshima09b} and \citepos{barker02} analyses, this analysis correctly predicts that (\ref{nat}b) conveys that the speaker stumbling through the junkyard would be stupid. What is asserted is that it is not the case that what the speaker did about stumbling through the junkyard was stupid. That the prejacent is negated (the speaker didn't stumble through the junkyard) follows, according to \citealt[249]{karttunen-etal2014}, from what is presupposed and what is asserted.

\citepos{karttunen-etal2014} analysis improves on previous ones because it is able to derive both attested interpretations. There are, however, two conceptual worries with the analysis. First, the analysis comes at a high cost: to derive the two interpretations, evaluative adjectives are systematically ambiguous. A second conceptual worry is that the analysis hard-wires into the two lexical entries an interaction between the projectivity of the prejacent and the projectivity of (what we refer to as) the generalization that would preferably fall out from a projection analysis. To illustrate, consider again the examples in (\ref{f2}a) and (\ref{nat}b). The generalization of (\ref{f2}a) is that the degree to which Feynman dancing on the table is stupid is higher than the contextual standard of {\em stupid}; that of (\ref{nat}b) is that the degree to which the speaker stumbling through the junkyard in the dark is stupid is higher than the contextual standard of {\em stupid}. (We motivate in section \ref{s2} that both the prejacent and the generalization are lexical entailments of EAS.) There is an interaction between the  prejacent and the generalization that has not yet been observed for projective content: when the prejacent projects, the generalization does not, as in (\ref{f2}b), and when the prejacent does not project, the generalization does, as in (\ref{nat}b). To illustrate that this interaction is specific to the projective content associated with EAS, consider (\ref{noint}a) with the factive predicate {\em discover}: what is typically taken to follow from (\ref{noint}a) is that the T.A.\ was cheating and that Sam discovered that the T.A.\ was cheating. As is well-known, the content of the complement of {\em discover} may project over negation, in which case (\ref{noint}b) means that the T.A.\ was cheating but that Sam didn't discover it. Crucially, when the content of the complement does not project over negation, that Sam discovered it does not project either: (\ref{noint}b) means that it is not the case that the T.A.\ was cheating and Sam discovered it, i.e., both contents of (\ref{noint}a) are interpreted in the scope of negation.

\begin{exe}
\ex\label{noint}
\begin{xlist}
\ex Sam discovered that the T.A.\ was cheating.
\ex Sam didn't discover that the T.A.\ was cheating.
\end{xlist}
\end{exe}
With EAS, by contrast, we observe an interaction between the projection of the prejacent and the generalization. This interaction is hard-wired into the lexical entries under \citepos{karttunen-etal2014} analysis: when the prejacent projects, as in the lexical entry {\em adj}$_1$ in (\ref{lex}a), the generalization does not, by virtue of following from the asserted content; and when the prejacent does not project, as in the lexical entry {\em adj}$_2$ in (\ref{lex}b), the generalization does, by virtue of being part of the presupposed content.

%A third conceptual worry with \citepos{karttunen-etal2014} analysis concerns a content we refer to as the evaluation: in NEASs, the evaluation is negated when the prejacent projects but counterfactual when the prejacent does not project: that is, the evaluation of (\ref{f2}a), where the prejacent projects, is that Feynman dancing on the table was stupid, whereas the evaluation of (\ref{nat}b), where the prejacent does not project, is that the speaker stumbling through the junkyard would be stupid. This behavior of the evaluation, too, is hard-wired into the lexical entries of \citepos{karttunen-etal2014} analysis: the negated evaluation follows from the presupposed prejacent and the negated assertion in the lexical entry {\em adj}$_1$ in (\ref{lex}a), whereas the counterfactual evaluation is directly coded as part of the presupposition in the lexical entry {\em adj}$_2$ in (\ref{lex}b).

The analysis of EAS we develop in section \ref{s2} correctly predicts the two attested interpretations of EASs, in contrast to analyses according to which the prejacent is lexically specified as a presupposition, and also avoids both of the conceptual worries with \citepos{karttunen-etal2014} analysis: there is a single lexical entry for each evaluative adjective and the observed interaction in the projection of the prejacent and the generalization falls out from the analysis. After developing the analysis in section \ref{s2}, we provide experimental evidence for two predictions in section \ref{s3} and provide tentative support for a third prediction in section \ref{s4}. {\bf We discuss two open issues in section \ref{s5} NEED TO ADJUST} and conclude the paper in section \ref{s6}.

\section{A question-based analysis of the projection of the prejacent}\label{s2}

In this section, we develop an analysis that correctly predicts that the prejacent of EAS can, but need not project, and that also captures the interaction between the projection of the prejacent and the generalization. In contrast to previous analyses, including that in \citealt{karttunen-etal2014}, our analysis does not assume that the prejacent projects because it is lexically specified as a presupposition.

There are currently several analyses on the market that derive the projection of utterance content.

Some, discussed above, derive projection from a lexical specification of the content as a presupposition (e.g., \citealt{heim83,vds92}). Others derive projection from a combination of conventionally specified alternatives and pragmatic mechanisms (e.g., \citealt{abusch02,abusch10,romoli2015})

 from default backgrounding (e.g.\ \citealt{abrusan2011,abrusan2016}) or from the
